Manifold Destiny - or how to rig an election

### 2024-01-05 index.qmd
newbefrev
sticker

# Manifold Destiny - or how to rig an election
**Based upon the ideas developed by Edward K. Solomon**
![](pngs/md.png)
tidyr

### Install and load packages
```{webr-r}
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install(c("AlgebraicHaploPackage","cowplot","broom","htmltools","combinat","DT","dplyr","purrr","magrittr","data.table","tidyr","plotly"))
library(ManifoldDestinyWASMP)
ls(package:ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
ls(package:ManifoldDestinyWASMD)
library(magrittr)
md <- ManifoldDestinyWASMD::metad
library(dplyr)
library(combinat)
library(htmltools)
library(ggplot2)
library(broom)
library(tidyr)
library(combinat)
library(AlgebraicHaploPackage)
```

>>>>

# Manifold Destiny - or how to rig an election
**Based upon the ideas developed by Edward K. Solomon**
![](pngs/md.png)

### Install and load packages
```{webr-r}
wasmconload()
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install(c("AlgebraicHaploPackage","cowplot","broom","htmltools","combinat","DT","dplyr","purrr","magrittr","data.table","tidyr","plotly"))
library(ManifoldDestinyWASMP)
ls(package:ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
ls(package:ManifoldDestinyWASMD)
library(magrittr)
md <- ManifoldDestinyWASMD::metad
library(dplyr)
library(combinat)
library(htmltools)
library(ggplot2)
library(broom)
library(tidyr)
library(combinat)
library(AlgebraicHaploPackage)
```

### 2024-01-05 presentation.qmd
sticker

```{r, echo=F, message=F, warning=F}
library(ManifoldDestiny)
library(ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
library(RefManageR)
library(huxtable)
modlat <- eqpar$meql
md <- ManifoldDestinyWASMD::metad
source(paste0(rprojroot::find_rstudio_root_file(),'/script/simulations.R'))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/applications.R'))
metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
```

>>>>

```{r, echo=F, message=F, warning=F}
ManifoldDestiny::wasmnonload()
metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
md <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/simulations.R'))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/R/applications.R'))
```
